---
title: "Single Step Genomic BLUP"
author: "Chris Stricker and Peter von Rohr"
date: "5/28/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Disclaimer
This website is a repository for the project called Single Step Genomic BLUP in Swiss Dairy Cattle. Any type of public documentation that will be produced in this project will be maded available here.


## Presentations

* Seventh Workshop of Swiss Animal Breeding Technology Platform (SABRE-TP) at ETH Zurich. June 06 2018. 
    + [Summary](https://charlotte-ngs.github.io/SingleStepGBLUP/20180606-sabretp-workshop-ethz/20180527-sabretp-unterlagen-tc.pdf) 
    + Slides ( [html](https://charlotte-ngs.github.io/SingleStepGBLUP/20180606-sabretp-workshop-ethz/20180606-sabretp-slides-cs-pvr.html) | [pdf](https://charlotte-ngs.github.io/SingleStepGBLUP/20180606-sabretp-workshop-ethz/20180606-sabretp-slides-cs-pvr.pdf) )


## Further developments

* Chris and Rohan are working on the approach of Vandenplas et al 2017. 
* Meeting planned towards the end of July / beginning of August



```{r, results='asis'}
cat(rmddochelper::get_latest_change(), "\n")
```

